### 2014-09-26 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Add PDF metadata
San Francisco: Edits to fire section

@@

Another simplification of the model is that the sources of the gas phase polyurethane and wood fuel have constant areas at fixed locations (five furniture items in the basement interior for the polyurethane fuel, and the exterior basement balcony for the wood fuel). The following lines define the source fires in the FDS input file:

@@

The heat of combustion of polyurethane and wood were specified as 26,200~kJ/kg and 16,400~kJ/kg, respectively, based on data provided in the SFPE Handbook~\cite{SFPE:Tewarson}. The heat of combustion quantifies the amount of energy released per unit mass of the fuel. The following text defines Eqs.~\ref{eq:fuel_polyurethane} and \ref{eq:fuel_wood} for an FDS input file with the desired fuel and reaction properties discussed above:

>>>>

% PDF metadata
\hypersetup{
  pdftitle={Simulation of a Basement Fire in a Wood Frame Residential Structure - San Francisco, CA},
  pdfauthor={Overholt, Kristopher J., Weinschenk, Craig G., and Madrzykowski, Daniel},
  pdfsubject={Insert abstract here.},
  pdfkeywords={insert; keywords; here}
}

@@

The heat of combustion of polyurethane and wood were specified as 26,200~kJ/kg and 16,400~kJ/kg, respectively, based on data provided in the SFPE Handbook~\cite{SFPE:Tewarson}. The heat of combustion quantifies the amount of energy released per unit mass of the fuel. The following text defines Eqs.~\ref{eq:fuel_polyurethane} and \ref{eq:fuel_wood} for an FDS input file with the two fuels and reaction properties discussed above:

Another simplification of the model is that the sources of the gas phase polyurethane and wood fuel have constant areas at fixed locations (five furniture items in the basement interior for the polyurethane fuel, and the exterior basement balcony for the wood fuel).

A time-dependent burning rate was specified for each of the fuel packages in terms of a fuel mass flux. The fuel mass flux is the amount of fuel vapor per unit area that is released from the surface of each fuel package shown in Fig.~\ref{fig:fuel_placement}. The specified time-dependent fuel mass flux for each fuel package corresponds to the HRRs that were described earlier. The HRR from each individual fuel package contributes to the total HRR shown in Fig.~\ref{fig:hrr}. FDS then determines the amount of combustion that occurs throughout the simulation based on the amount of available fuel and oxygen at a given location. The following lines define the fire surfaces for each fuel package in the FDS input file:

@@
